IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/conclusion.tex
slice up
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

We present a formal semantics which describes how to extend arbitrary languages
with language-based coarse-grained IFC. We provably show the security guarantees
TSNI and TINI non-interference, where the proof technique is parametrized on the
target language, and it is developed for two ubiquitous scheduling policies. In
addition, we provide conditions to securely refine our formal semantics to
consider optimizations required in practice. Finally, we describe extensions to
the core IFC language with more advanced concepts like labeled values, privileges,
and a notation of clearance, and therefore connecting it with existing
IFC implementations for Javascript, Haskell, and (in
less detail) proposing IFC for C.

With this work, we set a global framework which describes how ideas from
OS can be systematically applied in programming languages.

>>>>

We presented a formal semantics which describes how to extend arbitrary languages
with language-based coarse-grained IFC. We prove the security guarantees
TSNI and TINI, where the proof technique is parametrized on the
target language, for two scheduling policies. In
addition, we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice. Finally, we described extensions to
the core IFC language with more advanced concepts like labeled values, privileges,
and a notation of clearance, and therefore connecting it with existing
IFC implementations for Javascript, Haskell, and (in
less detail) proposing IFC for C.
